\section*{Abstract}

%\UG{I'd capitalise things that are named entities with respect 
%to the \SUMMA project, such as ``Evaluation Plan'', ``Demonstration and Validation Plan'', etc.}

This document \replace{contains}{lays out} the Evaluation Plan 
for the \SUMMA platform and \ins{its} use cases. 
It \replace{details the - covers}{provides} an overview of the evaluation planned, including functionality testing of the prototypes, user evaluation of the use cases, 
platform integration testing, and component-level evaluation. This deliverable D7.1: Evaluation Plan is a first iteration of three reports. It will be followed by D7.2, the Initial Evaluation Report in Month 18, and D7.3, the Final Evaluation Report at the end of the project, i.e. in Month 36.

\cut{%
The Demonstration and Validation Plan, of which this document is a first version and which will be the basis for the Initial Evaluation Report in Month 18, will support the development of the three use cases and their validation. %
}

% \UG{What is the Demonstration and Validation Plan? 
% Is that a deliverable? I can't find it in the list of deliverables. 
% If it is, what is its number? In my opinion the above paragraph can go entirely.}

Although this deliverable covers \SUMMA evaluation as a whole to provide an overview, specific technical evaluation of \SUMMA's individual components is 
\ins{covered} mainly \replace{dealt with within}{by} the 
technical \replace{WPs (WP3, WP4, WP5 and WP6}{work packages WP3--6}. 
\replace{However, validation of the SUMMA concept belongs to WP7}{WP7 focuses on user evaluation and ultimately targets validating the concepts 
that \SUMMA is built on} through real-world testing of the three use-case-based demonstrators.

% \UG{There is a contradiction between the paragraph above and the first paragraph that 
% needs to be resolved. The first paragraph says that technical evaluation at the component 
% level is layed out in this deliverable; at the end it says it's not really, because that's a matter of the other work packages.}

This report starts with an introduction, followed in section 2 by an overall description of the evaluation methodology, and an introduction of the V-model.

Technical testing is covered in Section 3, with a brief explanation of the verification phases, testing planned for the 10 different \SUMMA components and technical testing of the Integrated Platform.

User-centered evaluation is the focus of Section 4, outlining the plans to test \SUMMA components, Integrated Platform and functionality testing of the different prototype versions by the user partners. Finally, we describe our plans for usability evaluation of the three envisaged use cases.

